\subsubsection{Data Sources}
\label{subsubsec:sources}
Many different sources were found and integrated for the analysis of suitable locations for a restaurant. The community website Yelp was one of the most important data sources for the evaluations. The Yelp Fusion interface provides helpful information about existing restaurants and their quality or potential competitors.  Possible information is e.g. the number of restaurants, the name, the type of food, the number of ratings, the rating or the coordinates of the restaurant with latitude and longitude.  However, the storage time of Yelp data is limited, so a suitable infrastructure for data extraction and analysis should be available!
\newline
Buying Power is an important factor in the catering industry because \textit{`Depending on your gastronomy concept, you can decide what level of purchasing power is needed.'} \cite{locana}. It makes little sense to open a three-star restaurant in a social focus area or vice versa. A fast food business will not last long between high-end haute cuisine restaurants. In 2018, public television broadcast a study about the quality of life in Germany. These studies included different population, city, and quality reports, which were conducted through surveys or with reference to external sources. One of the studies contained information about buying power in the cities of Germany. The report led to an external provider who had published this survey \cite{buyingpower}. This evaluation was publicly available in the download portal of the website in portable document format and was very well suited to adapting for integration. This attribute complements the model to determine the price level for a restaurant.
\newline
It is absolutely necessary for our customers and later applications to know how much rent you have to pay per month in which location and whether you can afford the property for long term \cite{locana}. In the search for a rent index in Germany we first came across a publicly accessible statistic in .json format \cite{Sparda}. Unfortunately, these were only the average property prices. Thereupon an interface to a popular real estate platform \cite{ImmoScout} opens up the possibility to get more accurate and up-to-date rental and property prices to include them in our analyses and evaluations.
\newline
You need the population density if you want to address and win a large number of customers in a short time. For our analyses, the population density logically means a lot, because a fast food restaurant in rural areas, for example, is neglected, whereas a noble restaurant in a sparsely populated area could meet with a better response. For these data we found a statistics platform with an automatable integration possibility.\cite{destatis}

