\subsection{Usecase Description}
\label{subsec:usecase}
%Überleitung zur Use Case Beschreibung und die Fragestellung
SCHULPS are investors who own various restaurants around the world. SCHULPS is headquartered in India and operates various restaurants and catering services. Thanks to a long-term expansion policy in recent years, the investor is also represented in the rest of the world with numerous gastronomic offers. SCHULPS is now also planning to open a restaurant in Germany. An investment of 650,000 euros is planned, whereby the monthly turnover must be at least 40,000 euros. The type of offer has not yet been precisely defined, but should be explained in an understandable way. Since the existing restaurants of SCHULPS differ completely due to the multitude of countries and cultures, the German market is still largely unknown. After some research, SCHULPS became aware of THD's offer to use data from the World Wide Web to search for a suitable location. With the help of search engines and advanced programming techniques, the World Wide Web offers an incredible range of possibilities. The comparison portals and enterprise platforms are more concerned to give their contents into the hand of Communities for different reasons \cite{SocialBusiness}. This also creates more possibilities for access to the data and its evaluation and analysis. The evaluation refers thereby a large part to the differentiation between honestly meant evaluations and the so-called 'Fake News'.
THD has given SCHULPS the ability to analyze locations and ratings and make recommendations for a suitable location.
