\section{Introduction}
\label{sec:introduction}
%Allgemeine Einführung in das Thema
Nowadays lots of people want to realize their dream to start an own business - often its associated with a own restaurant. Therefor a well-conceived concept is absolutely necessary because you have to deal with a lot of different requirements in relation to the financial aspects, the siting and the customers. All these factors should be well-matched to have a unique feature as a restaurant and to be competitive. \newline
%Überleitung zu den Lösungsansätzen
The purpose of the thesis is to make a recommendation for a new restaurant business in Germany. Especially to find an appropriate city for opening a restaurant based on different facts and taking into account the financial framework conditions.
A good indicator to discover a new restaurant business is to analyze restaurants which already exist. In the meantime the world wide web and it's community platforms are inevitable. Customers can leave reviews and rate their restaurant visits online. One of this platforms with it's thousands of restaurants and other business cases is definitely Yelp. Yelp offers an API for developers which we accessed with self-developed python code to collect the restaurant data, e.g. the name, the rating, the city and the review count. But for a significant analysis there was more information needed. As a consequence we collected additional data to find more relevant key figures which could help to find a city. These are the data sets of all cities in Germany and their population as well as the data sets containing the buying power and the average rent for commercial real estate. The main idea was to combine all the mentioned key figures to create an own \ac{KPI} from it to find out the most appropriate cities in Germany for starting a restaurant business. To find out what type of restaurant business could be worthwile, the underrepresented restaurant categories for the most potential cities were analyzed. Furthermore we analyzed the user's text review's on yelp to get more insights about the preferations of the customers. Due to the fact that the menu of a restaurant is an important factor, we analyzed the menu's of one city to find out the most popular items and services. With self-developed python scripts we collected all the mentioned data and stored it in the Google Cloud Platform, more precisely in it's Datastore which is a NoSQL document database. From there it was possible to create a \pg{}‚ instance with the fully-managed relational database service, the so called Google Cloud SQL. For a significant analysis of the raw datasets it was necessary to clean it thoroughly. For this part we developed python scripts as well as different database queries. \newline
For the financial aspects we developed a formula to generate a specific turnover by using a benchmark. With this formula we searched for commercial real estate for sale and rent via the Immoscout API and checked their affordability.  
The method in this paper describes a recommended procedure for finding a restaurant in a city in Germany at a pre-defined financial framework with the help of publicly accessible data.