\section{Literature Synthesis}
\label{sec:synthesis}
Essentially there are many papers in the internet which are refering to the restaurant business but most of them either have a different point of view or are focussing on a specific part of it like the siting of a restaurant or the impact of online ratings.

Last-named aspect belongs to the paper from Havard Unversity\cite{CaseOfYelp}. In this the author writes about the significant influence of yelp user ratings on the revenue of restaurants from data of Washington’s State Department of Revenue and proves it with statistical models. This is definitely a good insight but focusses as mentioned on just one specific partition of the restaurant business. Further it was not possible to use restaurants revenues as a key figure for this thesis because there are no profits and losses published for independent restaurants in Germany. Only restaurant chains with a huge number of restaurant branches and a yearly turnover were available. Due to too vague estimate this was renounced for statistical purposes in this paper.

In the bachelor thesis \cite{Imatra} it's all about the market analysis of existing restaurants based on various research methods to discover new possible restaurant businesses. This approach relates to the evaluation of surveys for a part of Imatra's population with single questions and does not focus on online review platforms like yelp and its variety of attributes. In addition to that this paper it was not neccessary to find a suitable location because there aldready is one with Imatra, Finland.

In the paper \cite{SentimentAnalysis} the authors proposed a method to identify the sentiment tendency of each review on yelp based on a statistical model and to classify it to a specific type of restaurant. The analysis of this authors is based on the yelp challenge dataset and does not belong to a specific use case. We also used this approach for our paper and started to analyse the reviews with the yelp challenge dataset first. After that we collected the data from the yelp API with certain constrictions because it is only possible to collect three reviews per restaurant each in german and english and not more than 200 characters per text review. As previously mentioned, this paper refers to text analysis only it is just a small part of our paper.  


