\begin{abstract}
Many people have the ambition to be self-employed and want to start a restaurant business. However, to run a restaurant can be risky due to lots of different requirements. A well-conceived idea for a restaurant is necessary to be successful and competitive. 
The purpose of this thesis is to make a recommendation for a new restaurant business in Germany based on various data sources, especially from the community platform of Yelp, because it's database includes lots of different facts such as the restaurant name, the rating, the user's review and the location.
However, for a significant analysis more information is necessary. Therefor we collect other data like the population, buying power and rent average for commercial real estates of all cities in Germany. With a combination of these key figures we introduce a \ac{KPI} to find the most suitable cities in Germany to open a restaurant. Moreover, we conduct text mining on Yelp user reviews to get more insights about the existing restaurants and the customer preferences. Further to this the menu of existing restaurants for an example city is analyzed. Regarding financial aspects we use a benchmark of Germany's catering industry in order to calculate parameters to meet a given revenue target as well as to find affordable commercial real estates. As a result we provide a list of cities in Germany with good conditions to open a restaurant business and recommendations on which category and qualitative aspects should be considered. 
\keywords{Restaurant Reviews  \and Data Integration \and Benchmarking \and Decision Making \and Text Mining}
\end{abstract}