\subsection{Restaurant Dishes \& Services Analysis}
\label{subsec:menu}
Besides the question in which city a restaurant should be located or whether it is best to rent or buy it,
the question of the menu is one of the most essential topics when opening a restaurant.
\newline
The data collected from the menus provided information on the dishes offered by restaurants in a city,
the existing restaurant categories and the favourite dishes of a particular restaurant.
In addition, the services offered were collected and analyzed.
\newline
Like stated in \fullref{subsubsec:potential}, the metropolis \textbf{Bochum} has the most potential to get a good rating.
For this reason, the menus from \textbf{Bochum} were analyzed to make recommendations for possible menu items and service which a restaurants can offer
to increase the probability to obtain a good rating.
\newline
Another information from \fullref{sec:introduction} is that one of the underrepresented categories is \textit{Thai}.
This coincides with the analysis of the categories in Bochum, where \textit{Thai} is represented on place 17 of altogether 20 categories and only with two restaurants.\footnote{\fullref{app:category}}
Thus this category would be at least a first selection.
If one compares this now with \fullref{app:items} one notices that on place 5 and 6 the dishes \textit{fried noodles} and \textit{fried rice} stand with respectively 63 and 55 occurrences.
On the one hand these are dishes that can be directly connected with Thai cuisine,
but it is also noticeable that there are only two Thai restaurants but such a high number of \textit{fried noodles} and \textit{fried rice}.
This discovery can be interpreted that although there are restaurants offering these dishes, only a few of them actually originate from Thai cuisine.
As a result, one can recommend that if a Thai restaurant is opened, these two dishes should appear within the menu.
As you can see from \fullref{app:fav_items} the favorite dish in Bochum is the \textit{rumpsteak} with a total count of 7.
On place two is the \textit{mixed ice cream} with 4 occurrences.
From these Top 10 one can read that the people in Bochum attach great importance to different kinds of desserts.
That means if a Thai restaurant should be opened, it can be recommended to offer a larger dessert menu, because desserts are especially popular in Bochum.
\newline
% TODO finish it; services table
